Wireless service accounting based on Ethereum state channels - Master Thesis

### 2019-10-06 Paper.tex
Minor corrections

\vspace{0.35cm}
As exposed in \cite{spectrumnh} although radio spectrum
``\textit{is often
  referred to as a `scarce resource`}'' there are
spectrum management strategies
being researched to improve and
support a brand new model of services
into the market; in particular there are
multiple 5G\cite{5g} innovative projects and initiatives
that try to solve this using Software
Defined Network\cite{sdns}
and Network Function Virtualization\cite{nfv}.

@@

Since spectrum is a scarce resource, it can
be tokenized being suited this
way for blockchain/DLT technologies business models;
in addition, since
atmospheric spectrum can be considered a public
asset, it's managed at the end by nations' governments
and its licensing and management should feature
a high level of transparency and at the same time
allow for efficiency and fair-competition making it
feasible to model on public blockchain systems.

@@

A more recent project like Hotspot Me\cite{hotspotme}
and also very aligned with the technological demonstration
described in this document consist on using mobile
APIs to allow a users to share WiFi hotspot tethering
to users nearby in exchange for ETH supported by a
micro-payment channel contract.

>>>>

\vspace{0.35cm}
As exposed in \cite{spectrumnh} although radio spectrum
``\textit{is often
  referred to as a `scarce resource`}'' there are
spectrum management strategies
being researched to improve and
support a brand new model of services
into the market; in particular there are
multiple 5G\cite{5g} innovative projects and initiatives
that try to solve this challenges using Software
Defined Network\cite{sdns}
and Network Function Virtualization\cite{nfv}.

@@

Since spectrum is a scarce resource, it can
be tokenized being suited this
way for blockchain/DLT technologies business models;
in addition, since
atmospheric spectrum can be considered a public
asset, it's initially managed by nations' governments
and its licensing and commercial usage should feature
a high level of transparency and at the same time
allow for efficiency and fair-competition making it
feasible to model on public blockchain systems.

@@

A more recent project like Hotspot Me\cite{hotspotme}
and also very aligned with the technological demonstration
described in this document consist on using mobile
APIs to allow users to share WiFi hotspot tethering
to users nearby in exchange for ETH supported by a
micro-payment channel contract.
